\documentclass[9pt,a4paper]{article}
\usepackage[a4paper,margin=0.25in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,nosep,after=\vspace{-1pt}}
\renewcommand{\baselinestretch}{0.95}
\usepackage{titlesec}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\hypersetup{colorlinks=true,urlcolor=blue}

\titleformat{\section}{\Large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{0ex}{-0.4ex}

\begin{document}

%==================== HEADER ====================%
\begin{center}
    {\LARGE \textbf{Hanumantha Rao Madineni}} \\
    \href{mailto:madenenihanumanturao@gmail.com}{madenenihanumanturao@gmail.com} ~|~
    +91 93928 52185 ~|~
    \href{https://www.linkedin.com/in/madeneni}{linkedin.com/in/madeneni} ~|~
    \href{https://hanuman-portfolio.vercel.app}{hanuman-portfolio.vercel.app} \\
    Bhimavaram, India
\end{center}


%==================== EDUCATION ====================%
\begin{tcolorbox}[enhanced,sharp corners,colback=white,boxrule=0pt,frame hidden,
borderline south={0.5pt}{0pt}{black!50}]
\textbf{Education} \\[0.4ex]
\textbf{B.Tech – Computer Science Engineering} \\
SRKR Engineering College \textbullet~ Bhimavaram \hfill 08/2023 -- \textbf{Expected 08/2027} \\
CGPA: \textbf{9.52} \\[0.3ex]

\textbf{Full Stack Development Program} \\
NxtWave CCBP 4.0 Academy \textbullet~ Online \hfill 2023 -- Present
\end{tcolorbox}

%==================== SUMMARY ====================%
\begin{tcolorbox}[enhanced,sharp corners,colback=white,boxrule=0pt,frame hidden,
borderline south={0.5pt}{0pt}{black!50}]
\textbf{About Me} \\[0.5ex]
Full Stack MERN Developer with expertise in building scalable web applications and AI-powered products. 
Strong experience with \textbf{React.js}, \textbf{Node.js}, \textbf{Express.js}, and \textbf{MongoDB} for end-to-end development.
Experienced in integrating LLM APIs (Claude, Gemini) for production features. 
Proven track record: hackathon winner (3rd place with 100+ teams), database optimization (100x query speedup), background job processing with Bull Queue + Redis.
Actively seeking roles to build scalable backend systems and ship features end-to-end.
\end{tcolorbox}

%==================== TECHNICAL SKILLS ====================%
\begin{tcolorbox}[enhanced,sharp corners,colback=white,boxrule=0pt,frame hidden,
borderline south={0.5pt}{0pt}{black!50}]
\textbf{Technical Skills}

\small
\textbf{Languages:} JavaScript (ES6+), Python \\
\textbf{Frontend:} React.js, React Hooks, Context API, Redux, Tailwind CSS, Material-UI, Responsive Design \\
\textbf{Backend:} Node.js, Express.js, RESTful APIs, Socket.io, Bull Queue (background jobs) \\
\textbf{Databases:} MongoDB + Mongoose, Redis, MySQL, Database Indexing (14+ indexes), Query Optimization \\
\textbf{AI/LLM Integration:} Claude API, Gemini API, OpenAI API, zero-shot classification \\
\textbf{DevOps:} Docker, Docker-Compose, GitHub Actions, Vercel, Render, Railway \\
\textbf{Security:} JWT + Refresh Tokens, httpOnly Cookies, Zod Validation, XSS Prevention, Rate Limiting \\
\textbf{Tools:} Git, GitHub, npm, VS Code, Postman, MongoDB Atlas
\end{tcolorbox}

\end{tcolorbox}

%==================== EXPERIENCE ====================%
\begin{tcolorbox}[enhanced,sharp corners,colback=white,boxrule=0pt,frame hidden,
borderline south={0.5pt}{0pt}{black!50}]
\textbf{Experience}
\vspace{-0.4ex}

\textbf{MERN Stack Developer – Recipe Finder (Hackathon)} \hfill Oct 2025 \\
Led full-stack development of AI-powered recipe discovery platform using MERN stack with Claude API integration.
Optimized MongoDB queries with compound indexing, achieving \textbf{100x query speedup}. Designed Bull Queue-based background job system for async processing.
Secured \textbf{3rd place among 100+ teams} for architecture quality and feature completeness. \\
GitHub: \href{https://github.com/hanuman2005/recipe-finder}{github.com/hanuman2005/recipe-finder}
\end{tcolorbox}

%==================== PROJECTS ====================%
\begin{tcolorbox}[enhanced,sharp corners,colback=white,boxrule=0pt,frame hidden,
borderline south={0.9pt}{0pt}{black!50}]
\textbf{Projects}
\vspace{-0.3ex}

\textbf{1. 🍳 Recipe-Finder – AI-Powered Culinary Assistant (Hackathon Winner – 3rd Place)} \hfill
\href{https://recipe-finder-live.vercel.app}{Live} | 
\href{https://github.com/hanuman2005/recipe-finder}{GitHub}
\begin{itemize}[topsep=1pt]
  \item Built full-stack ingredient-based recipe discovery with \textbf{Claude API} for AI-powered ingredient substitutions (zero-shot classification).
  \item Implemented smart filters: cuisine, diet types (vegan, keto, gluten-free), equipment (induction, microwave, no-cook) using compound \textbf{MongoDB indexes}.
  \item Designed \textbf{Bull Queue + Redis} background job system: email notifications, image optimization, search indexing (4 async processors with custom retry strategies).
  \item Optimized database queries with 14 strategic indexes, reducing query time from 2–5 seconds to \textbf{<50ms (100x speedup)}.
  \item Implemented real-time comments + ratings system, user authentication (\textbf{JWT + httpOnly cookies}), and favorites management.
  \item \textbf{Tech:} React + Tailwind | Node.js + Express | MongoDB + Mongoose | Claude API | Bull Queue | Docker
\end{itemize} \vspace{0.3ex}

\textbf{2. ⚖️ Dark-Contract – Legal Clause \& Dark-Pattern Auditor} \hfill
\href{https://dark-contract.vercel.app}{Live} | 
\href{https://github.com/hanuman2005/dark-contract}{GitHub}
\begin{itemize}[topsep=1pt]
  \item Built AI-powered legal auditor using \textbf{Claude API zero-shot classification} to analyze T\&C text for predatory clauses in <5 seconds.
  \item Privacy Scorecard: Grades Indian apps (Zomato, Swiggy, Meesho, BYJU's) from A+ to F based on data transparency — fully shareable on social media.
  \item Visual alert dashboard converts dense legal language into intuitive icons: data tracking, hidden costs, auto-renewal traps, mandatory arbitration.
  \item Indian app database: 100+ T\&C scores with public browsing (no upload required) — fills gap left by Western-only ToS;DR tool.
  \item Integrated PDF parsing (\textbf{pdfplumber}) + web scraping (\textbf{Puppeteer}) for T\&C retrieval and Claude analysis.
  \item Consumer compliance: Ensures adherence to IT Act 2000 and Consumer Protection Act 2019 — enables true informed consent.
  \item \textbf{Tech:} React + Tailwind | Node.js + Express | MongoDB | Claude API | Puppeteer | Python (pdfplumber) | Render + Vercel
\end{itemize} \vspace{0.3ex}

\textbf{3. 🤝 Group Decision Resolver – Collaborative Decision-Making Platform} \hfill
\href{https://group-decision-resolver.vercel.app}{Live} | 
\href{https://github.com/hanuman2005/group-decision-resolver}{GitHub}
\begin{itemize}[topsep=1pt]
  \item Full-stack MERN application for real-time collaborative group decision making using \textbf{Socket.io} WebSocket synchronization.
  \item Implemented multiple decision models: majority vote, Borda count (ranked voting), Condorcet analysis for sophisticated group choices.
  \item Time-boxed poll system with auto-close, spam prevention via \textbf{JWT authentication}, and concurrent user testing (50+ users).
  \item Interactive results dashboard with live D3.js charts, decision history, and PDF report export capability.
  \item \textbf{Tech:} React + D3.js | Node.js + Socket.io | MongoDB | JWT authentication
\end{itemize} \vspace{0.3ex}

\textbf{4. 🎓 AI Wiki Quiz Generator – Automated Assessment Platform (Internship Assignment)} \hfill
\href{https://ai-wiki-quiz.vercel.app}{Live} | 
\href{https://github.com/hanuman2005/ai-wiki-quiz}{GitHub}
\begin{itemize}[topsep=1pt]
  \item Full-stack application converting Wikipedia articles into AI-generated interactive quizzes using \textbf{Gemini API} and \textbf{LangChain}.
  \item Backend: Designed \textbf{FastAPI} REST APIs with Wikipedia scraping, quiz generation, and storage in \textbf{MongoDB}.
  \item Frontend: React SPA with interactive quiz mode, real-time scoring, attempt history, and retry functionality with responsive design.
  \item Difficulty levels: Easy (factual recall) → Hard (synthesis questions) with dynamic question generation.
  \item Deployed end-to-end: frontend on \textbf{Vercel}, backend on \textbf{Railway}, with error handling and validation.
  \item \textbf{Tech:} FastAPI (Python) | React.js | Gemini API via LangChain | Beautiful Soup (web scraping) | MongoDB
\end{itemize}

\end{tcolorbox}

%==================== AWARDS ====================%
\begin{tcolorbox}[enhanced,sharp corners,colback=white,boxrule=0pt,frame hidden,
borderline south={0.5pt}{0pt}{black!50}]
\textbf{Awards \& Recognition} \\[0.5ex]
\textbf{3rd Place – Recipe-Finder Hackathon 2025} \\
Built full-stack MERN app with AI integration and database optimization. Beat 100+ teams. \\[0.25ex]
\textbf{3rd Place – DevOps Flowthon 2025} \\
Secured 3rd place among 100+ teams for end-to-end DevOps workflow. Won ₹8000. \\[0.25ex]
\textbf{5th Place – Amaravati Quantum Valley Hackathon 2025} \\
Team "The Matrix Minds" placed 5th in the Quantum Path Planning challenge.
\end{tcolorbox}

\end{document}